Comparing Generative Pre-trained Transformer Models to Physicians for Assigning Causes of Death from Verbal Autopsy: A Case Study of 6939 Deaths in Sierra Leone from 2019-2022

### 2024-09-04 manuscript/manuscript.tex
Move age range perf figs to appendix

\author[1]{\fnm{Areeba} \sur{Zubair}}\email{areeba.zubair@mail.utoronto.ca}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{fig-perf-agerange-adult.pdf}
\caption{Model performance for adult records by five-year age range for assigning CGHR-10 CODs.}\label{fig-perf-agerange-adult}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{fig-perf-cod-adult.pdf}
\caption{Model performance for adult records by COD. GPT-3.5, GPT-4, InterVA-5, and InSilicoVA model performance for assigning CGHR-10 CODs in the adult age group (12 to 69 Years) by COD. PCCC values are sorted by the highest to lowest PCCC for each COD. Only models with PCCC values within .05 of the highest and lowest PCCC are shown. Suicide is not notable due to a small sample size of 3.}\label{fig-perf-cod-adult}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{fig-perf-agerange-child.pdf}
\caption{Model performance for child records by five-year age range for assigning CGHR-10 CODs.}\label{fig-perf-agerange-child}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{fig-perf-agerange-neo.pdf}
\caption{Model performance for neonatal records by age range. GPT-3.5, GPT-4, InterVA-5, and InSilicoVA model performance for assigning CGHR-10 CODs in the neonatal age group (under 28 days) by five-year age ranges. PCCC values are sorted by the highest to lowest PCCC for each age range. Only models with PCCC values within .05 of the highest and lowest PCCC are shown.}\label{fig-perf-agerange-neo}
\end{figure}

@@

The following figures show the model performance by PCCC for all records and physician agreed records (Figure \ref{fig-perf-allvsagree}), and the performance of models by PCCC across sex for the adult (12 to 69 years), child (28 days to 11 years), and neonatal (under 28 days) age groups in Figures \ref{fig-perf-sex-adult}, \ref{fig-perf-sex-child}, and \ref{fig-perf-sex-neo} respectively.

@@

@@

@@

@@

\begin{table}[!htbp]
    \caption{CGHR-10 COD assignment from GPT-4 for records coded as neonatal infections by physicians}\label{tab-misclass}%
    \begin{tabular}{@{}ll@{}}
    \toprule
    GPT-4 Assigned Cause of Death (CGHR-10) & Records\\

>>>>

@@

\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{fig-perf-cod-adult.pdf}
\caption{Model performance for adult records by COD.}\label{fig-perf-cod-adult}
\end{figure}

@@

@@

@@

@@

\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{fig-perf-agerange-adult.pdf}
\caption{Model performance for adult records by five-year age range.}\label{fig-perf-agerange-adult}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{fig-perf-agerange-child.pdf}
\caption{Model performance for child records by five-year age range.}\label{fig-perf-agerange-child}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{fig-perf-agerange-neo.pdf}
\caption{Model performance for neonatal records by age range.}\label{fig-perf-agerange-neo}
\end{figure}

@@

\begin{table}[!htbp]
    \caption{GPT-4 CGHR-10 COD assignment for physician coded neonatal infections records.}\label{tab-misclass}%
    \begin{tabular}{@{}ll@{}}
    \toprule
    GPT-4 Assigned Cause of Death (CGHR-10) & Records\\
